---
title: "time_graph"
author: "Bas van der Burg"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{time_graph}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
# Introduction

If you are working on an erasmusladder project and want to easily generate some graphs this is the perfect package for you.
Below I show you how easy it is to generate a graph based on a package that is loaded in.


## First we need to load some libraries that are used in this package
```{r setup, message=FALSE, warning=FALSE}
library(graphify)
library(readr)
library(here)
library(tidyverse)
library(dplyr)
library(plotly)
```

After the libraries are loaded you can simply load in some data that is generated by an erasmusladder. 
After thsi you can call a graphify function to generate a nice looking graph.
```{r}
# load in some data
data_time <- read_csv(here("data", "example.csv"))

# Graph for Average trail duration per session per genotype
time_graph(data_time, column = quo(`Trial duration(s)`), "Average trail duration per session per genotype", "Duration (s)")
```
